Reproducibility in plant pathology: where do we stand and a way forward

### 2021-10-13 analysis/paper/paper.Rmd
Revise headings of sections to match Phytopath article
Use black for bars in figure 1

# Where do we stand in regards to reproducibility?

## Article selection

@@

## Scoring criteria

@@

## Statistical analysis

@@

## Findings

@@

# Are there good examples in plant pathology?

@@

# Best practices to enhance reproducible research

@@

# Data availability statement

@@

# Code availability statement

@@

# References

@@

rrpp <- import_notes()
theme_set(theme_classic())
A <- ggplot(rrpp, aes(y = as.factor(comp_mthds_avail))) +
  geom_bar() +
  ylab("Score") +
  xlab(NULL)

B <- ggplot(rrpp, aes(y = software_avail)) +
  geom_bar() +
  xlab(NULL) +
  ylab(NULL)

C <- ggplot(rrpp, aes(y = software_cite)) +
  geom_bar() +
  ylab("Score")

D <- ggplot(rrpp, aes(y = data_avail)) +
  geom_bar() +
  ylab(NULL)

>>>>

# Materials and Methods

## Article Selection

@@

## Scoring Criteria

@@

## Statistical Analysis

@@

# Results

@@

# Discussion

## Are There Good Examples?

@@

## Best Practices to Enhance Reproducible Research

@@

# Author Recommended Internet Resources

## Data

@@

## Code

@@

# Literature Cited

@@

rrpp <- import_notes()
theme_set(theme_classic())
A <- ggplot(rrpp, aes(y = as.factor(comp_mthds_avail))) +
  geom_bar(fill = "black") +
  ylab("Score") +
  xlab(NULL)

B <- ggplot(rrpp, aes(y = software_avail)) +
  geom_bar(fill = "black") +
  xlab(NULL) +
  ylab(NULL)

C <- ggplot(rrpp, aes(y = software_cite)) +
  geom_bar(fill = "black") +
  ylab("Score")

D <- ggplot(rrpp, aes(y = data_avail)) +
  geom_bar(fill = "black") +
  ylab(NULL)
